%% This file is part of Enblend.
%% Licence details can be found in the file COPYING.


\subsection[Information Options\commonpart]{\label{sec:information-options}%
  \genidx[\rangebeginlocation]{information options}%
  \genidx{options!information}%
  Information Options\commonpart}

\begin{codelist}
  \label{opt:help}%
  \optidx[\defininglocation]{--help}%
  \shoptidx{-h}{--help}%
  \genidx{help}%
\item[\itempar{-h \\ --help}]\itemend
  Print information on the command-line syntax and all available options, giving a boiled-down
  version of this manual.


  \label{opt:show-globbing-algorithms}%
  \optidx[\defininglocation]{--show-globbing-algorithms}%
  \genidx{algorithm!globbing}%
  \gensee{globbing algorithms}{algorithm, globbing}%
\item[--show-globbing-algorithms]\itemend
  Show all globbing algorithms.

  Depending on the build-time configuration and the operating system the binary may support
  different globbing algorithms.  See \sectionName~\fullref{sec:globbing-algorithms}.


  \label{opt:show-gpu-info}%
  \optidx[\defininglocation]{--show-gpu-info}%
  \genidx{GPU@\acronym{GPU}}%
  \genidx{OpenCL@\acronym{OpenCL}}%
  \genidx{GPU@\acronym{GPU}!information on}%
  \gensee{information!on \acronym{GPU}}{\acronym{GPU}, information}%
  \genidx{OpenCL@\acronym{OpenCL}!information on configuration}%
  \gensee{information!on \acronym{OpenCL} configuration}{\acronym{OpenCL}, information}%
\item[--show-gpu-info \restrictednote{\acronym{OpenCL}-enabled versions only.}]\itemend
  Print a list of all available \acronym{GPU}~devices under \acronym{OpenCL}~control on all
  accessible platforms, the current preferences, and then exit; it is the same enumeration that
  \begin{literal}
    \app{} --verbose --version
  \end{literal}
  reveals.  \exampleName~\ref{ex:opencl-config} shows a complete output.

  \begin{exemplar}
    \begin{maxipage}
      \begin{terminal}
        \$ \app{} --show-gpu-info \\
        Available, OpenCL-compatible platform(s) and their device(s) \\
        ~~- Platform \#1:~Advanced Micro Devices, Inc., \\
        ~~~~~~~~~~~~~~~~~AMD Accelerated Parallel Processing, \\
        ~~~~~~~~~~~~~~~~~OpenCL 1.2 AMD-APP (1526.3) \\
        ~~~~* no GPU devices found on this platform \\
        ~~- Platform \#2:~NVIDIA Corporation, \\
        ~~~~~~~~~~~~~~~~~NVIDIA CUDA, \\
        ~~~~~~~~~~~~~~~~~OpenCL 1.1 CUDA 6.5.51 \\
        ~~~~* Device \#1:~max.~1024 work-items \\
        ~~~~~~~~~~~~~~~~~1047872 KB global memory with 32 KB read/write cache \\
        ~~~~~~~~~~~~~~~~~48 KB dedicated local memory \\
        ~~~~~~~~~~~~~~~~~64 KB maximum constant memory \\
        ~~~~~~~~~~~~~~~~~Extensions: \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_khr\_byte\_addressable\_store \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_khr\_fp64 \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_khr\_gl\_sharing \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_khr\_global\_int32\_base\_atomics \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_khr\_global\_int32\_extended\_atomics \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_khr\_icd \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_khr\_local\_int32\_base\_atomics \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_khr\_local\_int32\_extended\_atomics \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_nv\_compiler\_options \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_nv\_copy\_opts \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_nv\_device\_attribute\_query \\
        ~~~~~~~~~~~~~~~~~~~~~cl\_nv\_pragma\_unroll \\
        ~~Search path (expanding ENBLEND\_OPENCL\_PATH and appending built-in path) \\
        ~~~~/usr/local/share/enblend/kernels:/usr/share/enblend/kernels \\
        Currently preferred GPU is device \#1 on platform \#2 (auto-detected).
      \end{terminal}
    \end{maxipage}

    \caption[Sample \acronym{OpenCL} configuration.]%
            {\label{ex:opencl-config}%
              A sample \acronym{OpenCL} configuration as detected by \App.}
  \end{exemplar}


  \label{opt:show-image-formats}%
  \optidx[\defininglocation]{--show-image-formats}%
  \genidx{format!image}%
  \gensee{image formats}{format, image}%
\item[--show-image-formats]\itemend
  Show all recognized image formats, their filename extensions and the supported per-channel
  depths.

  Depending on the build-time configuration and the operating system, the binary supports
  different image formats, typically: \acronym{BMP}, \acronym{EXR}, \acronym{GIF},
  \acronym{HDR}, \acronym{JPEG}, \acronym{PNG}, \acronym{PNM}, SUN, \acronym{TIFF},
  and~\acronym{VIFF} and recognizes different image-filename extensions, again typically:
  \filename{bmp}, \filename{exr}, \filename{gif}, \filename{hdr}, \filename{jpeg},
  \filename{jpg}, \filename{pbm}, \filename{pgm}, \filename{png}, \filename{pnm},
  \filename{ppm}, \filename{ras}, \filename{tif}, \filename{tiff}, and~\filename{xv}.

  The maximum number of different per-channel depths any \appcmd{} provides is seven:
  \begin{itemize}
  \item 8~bits unsigned integral -- \sample{uint8}
  \item 16~bits unsigned or signed integral -- \sample{uint16} or \sample{int16}
  \item 32~bits unsigned or signed integral -- \sample{uint32} or \sample{int32}
  \item 32~bits floating-point -- \sample{float}
  \item 64~bits floating-point -- \sample{double}
  \end{itemize}


  \label{opt:show-signature}%
  \optidx[\defininglocation]{--show-signature}%
  \genidx{signature}%
\item[--show-signature]\itemend
  Show the user name of the person who compiled the binary, when the binary was compiled, and on
  which machine this was done.

  This information can be helpful to ensure the binary was created by a trustworthy builder.


  \label{opt:show-software-components}%
  \optidx[\defininglocation]{--show-software-components}%
  \genidx{information!on software components}%
  \gensee{software!components}{information, on software components}%
  \genidx{dynamic-library environment}%
  \genidx{header files}%
\item[--show-software-components]\itemend
  Show the name and version of the compiler that built \App{} followed by the versions of all
  important libraries against which \App{} was compiled and linked.

  Technically, the version information is taken from header files, thus it is independent of the
  dynamic-library environment the binary runs within.  The library versions printed here can
  help to reveal version mismatches with respect to the actual dynamic libraries available to
  the binary.


  \label{opt:version}%
  \optidx[\defininglocation]{--version}%
  \shoptidx{-V}{--version}%
  \genidx{software!version}%
  \gensee{version}{software, version}%
  \gensee{binary version}{software, version}%
\item[\itempar{-V \\ --version}]\itemend
  Output information on the binary's version.

  Team this option with \flexipageref{\option{--verbose}}{opt:verbose} to show configuration
  details, like the extra features that may have been compiled in.  For details consult
  \sectionName~\fullref{sec:exact-version}.
\end{codelist}

\genidx[\rangeendlocation]{information options}


%%% Local Variables:
%%% fill-column: 96
%%% End:
