%% This file is part of Enblend.
%% Licence details can be found in the file COPYING.


\subsection[Expert Options]{Expert Options% Not a \commonpart!
  \label{sec:expert-options}
  \genidx[\rangebeginlocation]{expert options}
  \genidx{options!expert}}


%%% IMPLEMENTATION NOTE: This file is included in both manuals, but
%%% rendered differently by conditional inclusion; Enblend and Enfuse
%%% have different sets of ``Expert Options''.  Hence, the name prefix
%%% `common-', but no `\commonpart' sign.


\ifenblend
  Control inner workings of \app{} and in particular the
  interpretation of images.
\fi

\ifenfuse
  Control inner workings of \app{} and the reading\slash writing of
  weight masks.
\fi


\begin{codelist}
  \label{opt:fallback-profile}%
  \optidx[\defininglocation]{--fallback-profile}%
\item[--fallback-profile=\metavar{PROFILE-FILENAME}]\itemend Use the
  \acronym{ICC} profile in \metavar{PROFILE-FILENAME} instead of the
  default \acronym{sRGB}.\genidx{profile!fallback}\genidx{fallback
    profile} This option only is effective if the input images come
  \emph{without} color profiles \emph{and} blending is not performed
  in the trivial luminance interval\genidx{luminance interval!trivial}
  or \acronym{RGB}-cube.\genidx{RGB-cube@\acronym{RGB}-cube}

  Compare
  option~\flexipageref{\option{--blend-colorspace}}{opt:blend-colorspace}
  and Chapter~\fullref{sec:color-profiles} on color profiles.


  \label{opt:layer-selector}%
  \optidx[\defininglocation]{--layer-selector}%
  \genidx{layer selection}%
\item[--layer-selector=\metavar{ALGORITHM}]\itemend Override the
  standard layer selector algorithm~\sample{\val{val:layer-selector}}.

  \App{} offers the following algorithms:

  \begin{codelist}
  \item[all-layers\genidx{layer selection!all layers}]\itemend Select
    all layers in all images.

  \item[first-layer\genidx{layer selection!first layer}]\itemend
    Select only first layer in each multi-layer image.  For
    single-layer images this is the same as \sample{all-layers}.

  \item[last-layer\genidx{layer selection!last layer}]\itemend
    Select only last layer in each multi-layer image.  For
    single-layer images this is the same as \sample{all-layers}.

  \item[largest-layer\genidx{layer selection!largest-layer}]\itemend
    Select largest layer in each multi-layer image, where the
    ``largeness'', this is the size is defined by the product of the
    layer width and its height.  The channel width of the layer is
    ignored.  For single-layer images this is the same as
    \sample{all-layers}.

  \item[no-layer\genidx{layer selection!no layer}]\itemend Do not
    select any layer in any image.

    This algorithm is useful to temporarily exclude some images in
    response files.
  \end{codelist}


\ifenfuse
  \label{opt:load-masks}%
  \optidx[\defininglocation]{--load-masks}%
  \item[\itempar{--load-masks~\textrm{(\oldstylefirst~form)}
      \\ --load-masks=\metavar{SOFT-MASK-TEMPLATE}~\textrm{(\oldstylesecond~form)}
      \\ --load-masks=\metavar{SOFT-MASK-TEMPLATE}:\feasiblebreak
      \metavar{HARD-MASK-TEMPLATE}~\textrm{(\oldstylethird~form)}}]\itemend
    Load\genidx{mask!loading} \genidx{load mask} masks from images
    instead of computing them.

    The masks have to be a grayscale images.

    \begin{sloppypar}
      First form: Load all soft-weight masks from files that were
      previously saved with option~\option{--save-masks}.  If
      option~\option{--hard-mask} is effective only load hard masks.
      The respective defaults are
      \mbox{\code{\val{val:default-soft-mask-template}}} and
      \mbox{\code{\val{val:default-hard-mask-template}}}.\genidx{filename
        template} \genidx{mask!filename template} In the second form,
      \metavar{SOFT\hyp{}MASK\hyp{}TEMPLATE} defines the names of the
      soft-mask files.  In the third form,
      \metavar{HARD\hyp{}MASK\hyp{}TEMPLATE} additionally defines the
      names of the hard-mask files.  See option~\option{--save-masks}
      below for the description of mask templates.
    \end{sloppypar}

    Options~\option{--load-masks} and~\option{--save-masks} are
    mutually exclusive.
\fi


  \label{opt:parameter}%
  \optidx[\defininglocation]{--parameter}%
\item[--parameter=\metavar{KEY}\optional{=\metavar{VALUE}}\optional{:\dots}]\itemend
  Set a \metavar{KEY}-\metavar{VALUE} pair, where \metavar{VALUE} is
  optional.  This option is cumulative.  Separate multiple pairs with
  the usual numeric delimiters.

  This option has the negated form
  \sample{--no-parameter},\optidx[\defininglocation]{--no-parameter}
  which takes one or more \metavar{KEY}s and removes them from the
  list of defined parameters.  The special key~\sample{*} deletes all
  parameters at once.

  Parameters allow the developers to change the internal workings of
  \App{} without the need to recompile or relink.


\ifenblend
  \label{opt:pre-assemble}%
  \optidx[\defininglocation]{--pre-assemble}%
  \shoptidx{-a}{--pre-assemble}%
  \item[\itempar{-a \\ --pre-assemble}]\itemend
    Pre-assemble non-overlapping images before each blending
    iteration.

    This overrides the default behavior which is to blend the images
    sequentially in the order given on the command line.  \App{} will
    use fewer blending iterations, but it will do more work in each
    iteration.

    This option has the negated form
    \sample{--no-pre-assemble},\optidx[\defininglocation]{--no-pre-assemble}
    which restores the default.
\fi


  \label{opt:prefer-gpu}%
  \optidx[\defininglocation]{--prefer-gpu}%
\item[--prefer-gpu=\optional{\metavar{PLATFORM}:}\metavar{DEVICE}
  \restrictednote{\acronym{OpenCL}-enabled versions only.}]\itemend
  Direct \App{} towards a particular \acronym{OpenCL}\genidx{OpenCL}
  \metavar{DEVICE}\genidx{OpenCL!device} on the first autodetected
  \metavar{PLATFORM}\genidx{OpenCL!platform} or directly to the given
  \metavar{PLATFORM}\slash\metavar{DEVICE} combination.  Use the
  numbers of platform and device found either with
  \begin{terminal}
    \$ \app{} --verbose --version
  \end{terminal}
  or
  \begin{terminal}
    \$ \app{} --show-gpu-info
  \end{terminal}
  Note that this option only selects \acronym{GPU}-devices; it does
  not \emph{activate} any, use
  option~\flexipageref{\option{--gpu}}{opt:gpu} for that.

  When told to employ the \acronym{GPU}\genidx{GPU} with
  \sample{--gpu}, by default \App{} uses the first device on the first
  autodetected platform it finds via queries of the
  \acronym{OpenCL}\genidx{GPU} subsystem, where neither the device,
  nor the platform may be the ones the user wants.  Usually she will
  select the device with the highest performance, maximum possible
  number of work-items, and largest associated memory.


\ifenblend
  \label{opt:x}%
  \optidx[\defininglocation]{-x}%
  \item[-x] Checkpoint\genidx{checkpoint results}
    \genidx{result!checkpoint} partial results to the output file
    after each blending step.
\fi


\ifenfuse
  \label{opt:save-masks}%
  \optidx[\defininglocation]{--save-masks}%
  \item[\itempar{--save-masks~\textrm{(\oldstylefirst~form)}
      \\ --save-masks=\metavar{SOFT-MASK-TEMPLATE}~\textrm{(\oldstylesecond~form)}
      \\ --save-masks=\metavar{SOFT-MASK-TEMPLATE}:\feasiblebreak
      \metavar{HARD-MASK-TEMPLATE}~\textrm{(\oldstylethird~form)}}]\itemend
    Save\genidx{mask!save}\genidx{save mask} the generated weight
    masks to image files.

    \begin{sloppypar}
      First form: Save all soft-weight masks in files.  If
      option~\option{--hard-mask} is effective also save the hard
      masks.  The defaults are
      \code{\val{val:default-soft-mask-template}} and
      \code{\val{val:default-hard-mask-template}}.\genidx{filename
        template}\genidx{mask!filename template} In the second form,
      \metavar{SOFT\hyp{}MASK\hyp{}TEMPLATE} defines the names of the
      soft-mask files.  In the third form,
      \metavar{HARD\hyp{}MASK\hyp{}TEMPLATE} additionally defines the
      names of the hard-mask files.
    \end{sloppypar}

    \App{} will stop after saving all masks unless
    option~\option{--output} is given, too.  With both options given,
    this is, \sample{--save-masks} and \sample{--output}, \App{} saves
    all masks and then proceeds to fuse the output image.\genidx{save
      mask!only}\genidx{only save mask}

    Both \metavar{SOFT\hyp{}MASK\hyp{}TEMPLATE} and
    \metavar{HARD\hyp{}MASK\hyp{}TEMPLATE} define templates that are
    expanded for each mask file.  In a template a percent sign
    (\sample{\%}) introduces a variable part.  All other characters
    are copied literally.  Lowercase letters refer to the name of the
    respective input file, whereas uppercase ones refer to the name of
    the output file.  Table~\fullref{tab:mask-template-characters}
    lists all variables.

    A fancy mask filename template could look like this:
    \begin{literal}
      \%D/mask-\%02n-\%f.tif
    \end{literal}
    It puts the mask files into the same directory as the output file
    (\sample{\%D}), generates a two-digit index (\sample{\%02n}) to
    keep the mask files nicely sorted, and decorates the mask filename
    with the name of the associated input file (\sample{\%f}) for easy
    recognition.

    Options~\option{--load-masks} and~\option{--save-masks} are
    mutually exclusive.
\fi
\end{codelist}


\ifenfuse
  \input{common-mask-template-characters}
\fi

\genidx[\rangeendlocation]{expert options}
