%% This file is part of Enblend.
%% Licence details can be found in the file COPYING.


\chapter[Seam Generators]{Seam Generators
  \label{sec:seam-generators}
  \genidx[\rangebeginlocation]{seam generation}}

This version of \App{} supports two main algorithms to generate seam
lines.  Use
option~\option{--primary-seam-generator}=\metavar{ALGORITHM} to select
one of the generators.

\begin{description}
  \genidx[\summarylocation]{seam generation}%
  \genidx{nearest feature transform}%
  \gensee{NFT@\acronym{NFT}}{nearest feature transform}%
\item[\itempar{Nearest Feature Transform (\acronym{NFT}),
    \metavar{ALGORITHM}=\code{nearest-feature-transform}}]\itemend
  The Nearest
  Feature Transform\footnote{\propername{Muhammad H. Alsuwaiyel}%
    \genidx{Alsuwaiyel, Muhammad@\propername{Alsuwaiyel, Muhammad H.}}
    and \propername{Marina Gavrilova}%
    \genidx{Gavrilova, Marina@\propername{Gavrilova, Marina}}, ``On
    the Distance Transform of Binary Images'', Proceedings of the
    International Conference on Imaging Science, Systems, and
    Technology, June 2000, \abbreviation{Vols.\ } I and II, pages
    83--86.}, also known as
  \uref{\wikipediadistancetransform}{Distance
    Transform}\genidx{distance transform}
  (\acronym{DT})\gensee{DT@\acronym{DT}}{distance transform}, is a
  fast and efficient technique to produce a seam line route given the
  geometries of multiple overlapping images.

  \acronym{NFT} as implemented in this version of \App{} only takes
  into account the \emph{shape of the overlap area.}  It completely
  ignore the images' contents.

  \genidx{graph-cut algorithm}%
  \gensee{GC@\acronym{GC}}{graph-cut algorithm}%
\item[\itempar{Graph-Cut (\acronym{GC}),
    \metavar{ALGORITHM}=\code{graph-cut}}]\itemend
  \uref{\wikipediagraphcuts}{Graph-Cut} is a region-oriented way of
  segmenting images.

  The generator is based on the idea of finding a minimum cost ``cut''
  of a graph created from a given image pair.  A ``cut'' is where the
  seam line appears.  \acronym{GC} determines the cost from the
  overlapping images' contents.
\end{description}

\noindent The most significant difference between the two algorithms
is the output mask gradation.\genidx{seam generation!details}
\acronym{NFT} produces a coarse approximation of the seam, running as
far away from the overlap-region borders as possible.  The resulting
mask could then be blended as-is, however, \App{} by default runs
image-content dependent optimizers to increase the mask gradation and
for example omits the regions where the images differ.  The result is
a finer seam line, which only loosely follows the shape of
\acronym{NFT}'s primary seam.

Graph-Cut,\genidx{graphcut!details} on the other hand, is capable of
producing the final mask in one pass without the need of further
optimizers.  It looks for a seam line that is \emph{globally} optimal,
taking into account feature frequency, as well as image dissimilarity.
This means, the seam is less likely to cross lines like for example
fences, lampposts, or road markings, where they would be visible.

The optimizers which run after \acronym{NFT} can also be run after
\acronym{GC}.  Nevertheless, \acronym{GC} works best just with a fine
mask (option~\option{--fine-mask}); optimizers are then automatically
\emph{turned off} to take full advantage of the detailed seam
\acronym{GC} produces.

\acronym{GC} requires more memory and computation time to complete
than \acronym{NFT}.  Thus, it is best to prefer \acronym{NFT} where
the images used are large and execution time is crucial.  If quality
is the priority, using \acronym{GC} and fine mask usually produces
visually more pleasing results.

\acronym{GC} is currently limited\genidx{graphcut!limitations} to
seams that begin and end on the images' borders.  This means that the
algorithm cannot run in cases where, for example, one image is
contained in another, resulting in a loop-like seam.  In such cases,
though, \App{} automatically falls back to a \acronym{NFT}-generated
seam, making its application transparent to the user.

\genidx[\rangeendlocation]{seam generation}
