%% This file is part of Enblend.
%% Licence details can be found in the file COPYING.


\subsection[Expert Mask Generation Options]{\label{sec:expert-mask-generation-options}%
  \genidx[\rangebeginlocation]{expert mask generation options}%
  \genidx{options!mask generation for experts}%
  Expert Mask Generation Options}

These options allow for a detailed control of the seam-line optimizers which govern the mask
generation.

\begin{codelist}
  \label{opt:anneal}%
  \optidx[\defininglocation]{--anneal}%
  \genidx{optimize!anneal parameters}%
  \gensee{anneal parameters}{optimize, anneal parameters}%
  \genidx{optimizer!simulated annealing}%
  \gensee{simulated annealing optimizer}{optimizer, simulated annealing}%
\item[--anneal=\metavar{TAU}\optional{:\metavar{DELTA-E-MAX}\optional{:\metavar{DELTA-E-MIN}\optional{:\metavar{K-MAX}}}}]\itemend
  Set the parameters of the Simulated Annealing optimizer.  See
  \tableName~\fullref{tab:optimizer-strategies}.

  \begin{codelist}
  \item[\metavar{TAU}] \metavar{TAU} is the temperature reduction factor in the Simulated
    Annealing; it also can be thought of as ``cooling factor''.  The closer \metavar{TAU} is to
    one, the more accurate the annealing run will be, and the longer it will take.

    Append a percent sign (\sample{\%}) to specify \metavar{TAU} as a percentage.

    Valid range: $\val{val:minimum-anneal-tau} < \metavar{TAU} < \val{val:maximum-anneal-tau}$.

    The default is \val{val:default-anneal-tau}; values around 0.95 are reasonable.  Usually,
    slower cooling results in more converged points.

  \item[\metavar{DELTA-E-MAX}, \metavar{DELTA-E-MIN}]\itemend \metavar{DELTA-E-MAX} and
    \metavar{DELTA-E-MIN} are the maximum and minimum cost change possible by any single
    annealing move.

    Valid range: $\val{val:minimum-anneal-deltae-min} < \metavar{DELTA-E-MIN} <
    \metavar{DELTA-E-MAX}$.

    In particular they determine the initial and final annealing temperatures according to:

    \begin{align*}
      T_{\mathrm{initial}} &= \frac{\metavar{DELTA-E-MAX}}{\log(\metavar{K-MAX} / (\metavar{K-MAX} - 2))} \\
      T_{\mathrm{final}} &= \frac{\metavar{DELTA-E-MIN}}{\log(\metavar{K-MAX}^2 - \metavar{K-MAX} - 1)}
    \end{align*}

    The defaults are: \metavar{DELTA-E-MAX}: \val{val:default-anneal-deltae-max} and
    \metavar{DELTA-E-MIN}: \val{val:default-anneal-deltae-min}.

  \item[\metavar{K-MAX}]\itemend \metavar{K-MAX} is the maximum number of ``moves'' the
    optimizer will make for each line segment.  Higher values more accurately sample the state
    space, at the expense of a higher computation cost.

    Valid range: $\metavar{K-MAX} \geq \val{val:minimum-anneal-kmax}$.

    The default is \val{val:default-anneal-kmax}.  Values around 100 seem reasonable.
  \end{codelist}


  \label{opt:dijkstra}%
  \optidx[\defininglocation]{--dijkstra}%
  \genidx{radius!\propername{Dijkstra}}%
  \gensee{Dijkstra@\propername{Dijkstra} radius}{radius, \propername{Dijkstra}}%
\item[--dijkstra=\metavar{RADIUS}]\itemend
  Set the search \metavar{RADIUS} of the \propername{Dijkstra} Shortest Path algorithm used in
  \propername{Dijkstra} Optimization (see \tableName~\fullref{tab:optimizer-strategies}).

  A small value prefers straight line segments and thus shorter seam lines.  Larger values
  instruct the optimizer to let the seam line take more detours when searching for the best seam
  line.

  Valid range: $\metavar{RADIUS} \geq \val{val:minimum-dijkstra-radius}$.

  Default: \val{val:default-dijkstra-radius}~pixels.


  \label{opt:image-difference}%
  \optidx[\defininglocation]{--image-difference}%
  \genidx{image difference}%
  \genidx{difference image}%
\item[\itempar{--image-difference=\metavar{ALGORITHM}\optional{:\feasiblebreak
      \metavar{LUMINANCE-WEIGHT}\optional{:
        \feasiblebreak\metavar{CHROMINANCE-WEIGHT}}}}]\itemend

  \App{} calculates the difference of a pair of overlapping color images when it generates the
  primary seam with a Graph-Cut and also before it optimizes the seams.  It employs a
  user-selectable \metavar{ALGORITHM} that is controlled by the

  \begin{itemize}
    \genidx{weight!luminance}%
    \gensee{luminance weight}{weight, luminance}%
  \item
    weights for luminance differences, \metavar{LUMINANCE-WEIGHT},
    $w_{\mathrm{luma}}$ and

    \genidx{weight!chrominance}%
    \gensee{chrominance weight}{weight, chrominance}%
  \item
    color differences, \metavar{CHROMINANCE-WEIGHT}, $w_{\mathrm{chroma}}$.
  \end{itemize}

  For black-and-white images the difference is simple the absolute difference of each pair of
  pixels.

  \begin{codelist}
    \genidx{maximum hue-luminance}%
    \genidx{hue-luminance maximum}%
    \genidx{luminance-hue maximum}%
  \item[\itempar{maximum-hue-luminance \\ maximum-hue-lum
      \\ max-hue-luminance \\ max-hue-lum \\ max}]\itemend Calculate
    the difference~$d$ as the maximum of
    the differences of the luminances~$l$ and hues~$h$ of each pair
    of pixels $P_1$ and $P_2$:
    \[
    d  = \max\left(w_{\mathrm{luma}} \times |l(P_1) - l(P_2)|,
    w_{\mathrm{chroma}} \times |h(P_1) - h(P_2)|\right).
    \]

    This algorithm was the default for \App{} up to version~4.0.

    \genidx{delta-E}%
    \genidx{colorspace!\acronym{L*a*b*}}%
  \item[\itempar{delta-e \\ de}]\itemend
    Calculate the difference~$d$ as the \propername{Euclidean} distance of the pixels in
    \acronym{L*a*b*} space:

    \begin{align*}
      d = \Big[ & w_{\mathrm{luma}} \times \left(L(P_1) - L(P_2)\right)^2 + \\
                & w_{\mathrm{chroma}} \times \left(a(P_1) - a(P_2)\right)^2 + \\
                & w_{\mathrm{chroma}} \times \left(b(P_1) - b(P_2)\right)^2
        \Big]^{1/2}
    \end{align*}

    This is the default in \App{} version~4.1 and later.

    Note that the ``delta-E'' mentioned here has nothing to do with \metavar{DELTA-E-MAX} and
    \metavar{DELTA-E-MIN} of option~\flexipageref{\option{--anneal}}{opt:anneal}.
  \end{codelist}

  \begin{sloppypar}
    Both \metavar{LUMINANCE\hyp{}WEIGHT} and \metavar{CHROMINANCE\hyp{}WEIGHT} are non-negative.
    \App{} automatically normalizes the sum of \metavar{LUMINANCE\hyp{}WEIGHT} and
    \metavar{CHROMINANCE\hyp{}WEIGHT} to one.  Thus,
  \end{sloppypar}

  \begin{literal}
    --image-difference=delta-e:2:1
  \end{literal}

  and

  \begin{literal}
    --image-difference=delta-e:0.6667:0.3333
  \end{literal}

  define the same weighting function.

  The default \metavar{LUMINANCE\hyp{}WEIGHT} is \val{val:default-luminance-difference-weight}
  and the default \metavar{CHROMINANCE\hyp{}WEIGHT} is
  \val{val:default-chrominance-difference-weight}.

  \genidx{quality!match}%
  \gensee{match quality}{quality, match}%
  \gensee{image match quality}{quality, match}%
  At higher verbosity levels \App{} computes the true size of the overlap area in pixels and it
  calculates the average and standard deviation of the difference per pixel in the normalized
  luminance interval~$(0\dots1)$.  These statistical measures are based on \metavar{ALGORITHM},
  therefore they should only be compared for identical \metavar{ALGORITHM}s.  The average
  difference is a rough measure of quality with lower values meaning better matches.


  \label{opt:mask-vectorize}%
  \optidx[\defininglocation]{--mask-vectorize}%
  \genidx{mask!vectorization distance}%
  \gensee{vectorization distance}{mask, vectorization distance}%
\item[--mask-vectorize=\metavar{DISTANCE}]\itemend
  Set the mask vectorization \metavar{DISTANCE} that \App{} uses to partition each seam.  Thus,
  break down the seam to segments of length \metavar{DISTANCE} each.

  If \App{} uses a coarse mask (\flexipageref{\option{--coarse-mask}}{opt:coarse-mask}) or
  \App{} optimizes (\flexipageref{\option{--optimize}}{opt:optimize}) a mask it vectorizes the
  initial seam line before performing further operations.  See
  \tableName~\ref{tab:mask-generation} for the precise conditions.  \metavar{DISTANCE} tells
  \App{} how long to make each of the line segments called vectors here.

  The unit of \metavar{DISTANCE} is pixels unless it is a percentage as explained in the next
  paragraph.  In fine masks one mask pixel corresponds to one pixel in the input image, whereas
  in coarse masks one pixel represents for example \val{val:default-coarseness-factor}~pixels in
  the input image.

  Append a percentage sign (\sample{\%}) to \metavar{DISTANCE} to specify the segment length as
  a fraction of the diagonal of the rectangle including the overlap region.  Relative measures
  do not depend on coarse or fine masks, they are recomputed for each mask.  Values around
  5\%--10\% are good starting points.

  This option strongly influences the mask generation process!  Large \metavar{DISTANCE} values
  lead to shorter, straighter, less wiggly, less baroque seams that are on the other hand less
  optimal, because they run through regions of larger image mismatch instead of avoiding them.
  Small \metavar{DISTANCE} values give the optimizers more possibilities to run the seam around
  high mismatch areas.

  \genidx{seam line!loops}%
  \gensee{loops in seam line}{seam line, loops}%
  What should \emph{never} happen though, are loops or cusps in the seam line.  Counter loops
  and cusps with higher weights of \metavar{DISTANCE-WEIGHT}
  (option~\flexipageref{\option{--optimizer-weights}}{opt:optimizer-weights}), larger
  vectorization \metavar{DISTANCE}s, and \metavar{TAU}s
  (option~\flexipageref{\option{--anneal}}{opt:anneal}) that are closer to one.  Use
  option~\flexipageref{\option{--visualize}}{opt:visualize} to check the results.

  Valid range: $\metavar{DISTANCE} \geq \val{val:minimum-vectorize-distance}$.

  \App{} limits \metavar{DISTANCE} so that it never gets below
  \val{val:minimum-vectorize-distance} even if it has been given as a percentage.  The user will
  be warned in such cases.

  Defaults: \val{val:coarse-mask-vectorize-distance}~pixels for coarse masks and
  \val{val:fine-mask-vectorize-distance}~pixels for fine masks.


  \label{opt:optimizer-weights}%
  \optidx[\defininglocation]{--optimizer-weights}%
  \genidx{weight!optimizer}%
  \gensee{optimizer weights}{weight, optimizer}%
  \genidx{seam optimization}%
\item[--optimizer-weights=\metavar{DISTANCE-WEIGHT}\optional{:\metavar{MISMATCH-WEIGHT}}]\itemend
  Set the weights of the seam-line optimizer.  If omitted, \metavar{MISMATCH-WEIGHT} defaults to
  1.

  The seam-line optimizer considers two qualities of the seam line:

  \begin{itemize}
  \item
    The distance of the seam line from its initial position, which has been determined by
    \acronym{NFT} (see option~\flexipageref{\option{--no-optimize}}{opt:optimize}).

  \item
    The total ``mismatch'' accumulated along it.
  \end{itemize}

  \metavar{DISTANCE-WEIGHT} and \metavar{MISMATCH\hyp{}WEIGHT} define how to weight these two
  criteria.  \App{} up to version~3.2 used 1:1.  This version of \App{} uses
  \val{val:default-optimizer-weight-distance}:\val{val:default-optimizer-weight-mismatch}.

  A large \metavar{DISTANCE-WEIGHT} pulls the optimized seam line closer to the initial
  position.  A large \metavar{MISMATCH\hyp{}WEIGHT} makes the seam line go on detours to find a
  path along which the mismatch between the images is small.  If the optimized seam line shows
  cusps or loops (see option~\flexipageref{\option{--visualize}}{opt:visualize}), reduce
  \metavar{MISMATCH\hyp{}WEIGHT} or increase \metavar{DISTANCE\hyp{}WEIGHT}.

  Both weights must be non-negative.  They cannot be both zero at the same time.  Otherwise,
  their absolute values are not important as \App{} normalizes their sum.


  \label{opt:primary-seam-generator}%
  \optidx[\defininglocation]{--primary-seam-generator}%
  \genidx{generator!seam}%
  \genidx{seam!primary generator}%
  \gensee{primary seam generator}{seam, primary generator}%
\item[--primary-seam-generator=\metavar{ALGORITHM}]\itemend
  Select the algorithm responsible for generating the general seam route.

  This is the \metavar{ALGORITHM} that produces an initial seam line, which serves as the basis
  for later, optional optimizations.  Nearest Feature Transform (\acronym{NFT}) is the only
  algorithm up to and including \App{} version~4.0.  Version~4.1 added a Graph-Cut
  (\acronym{GC}) algorithm, which is the default for version~4.2 and later.

  Valid \metavar{ALGORITHM} names are:

  \begin{center}
    \begin{tabular}{p{.45\linewidth}l}
      \code{nearest-feature-transform}, \code{nft}\genidx{nearest
        feature transform (\acronym{NFT})} & Nearest Feature Transform \\
    \code{graph-cut}, \code{gc}\genidx{graph-cut (\acronym{GC})} &
    Graph-Cut
    \end{tabular}
  \end{center}

  See \chapterName~\fullref{sec:seam-generators} for details on \App's primary seam generators.
\end{codelist}

\genidx[\rangeendlocation]{expert mask generation options}


%%% Local Variables:
%%% fill-column: 96
%%% End:
