%% This file is part of Enblend.
%% Licence details can be found in the file COPYING.


\chapter[Weighting Functions]{\label{sec:weighting-functions}%
  \genidx[\rangebeginlocation]{weighting functions}%
  \genidx{exposure weighting!functions}%
  Weighting Functions}

As has been noted in the introductory \flexipageref*{Overview}{sec:overview}, \App{} supports
four different types of weighting.  The following sections describe the concept of weighting and
all weighting functions in detail.


\section[Weighting Pixels]{\label{sec:weighting-pixels}%
  \genidx{weighting!general concept of}%
  Weighting Pixels}

Image fusion maps each pixel~$P(i, x, y)$ of every input image~$i$ to a single pixel~$Q(x, y)$
in the output image:
\[
    P(i, x, y) \rightarrow Q(x, y),
\]
\noindent where $x$ runs from~1 to the width of the images, $y$ from~1 to the height, and $i$
from~1 to the number~$n$ of input images.

\begin{equation}
  \label{equ:weight}
  w(P(1, x, y)) P(1, x, y) + \ldots + w(P(n, x, y)) P(n, x, y)
  \rightarrow
  Q(x, y),
\end{equation}
\noindent where

\begin{itemize}
\item
  each $w$ is non-negative to yield a physical intensity and

\item
  the sum of all $w$ is 1 to leave the total intensity unchanged.
\end{itemize}

\noindent The pixel weights~$w$ themselves are weighted sums with the same constraints

\begin{align*}
    w(P) = \;
    & w_{\mathrm{exp}} \; f_{\mathrm{exp}}(P) + \\
    & w_{\mathrm{sat}} \; f_{\mathrm{sat}}(P) + \\
    & w_{\mathrm{cont}} \; f_{\mathrm{cont}}(P, r_{\mathrm{cont}}) + \\
    & w_{\mathrm{ent}} \; f_{\mathrm{ent}}(P, r_{\mathrm{ent}}).
\end{align*}

\noindent Here we have abbreviated $P(i, x, y)$ to $P$ for simplicity.  The user defines the
constants~$w_{\mathrm{exp}}$, $w_{\mathrm{sat}}$, $w_{\mathrm{cont}}$, and $w_{\mathrm{ent}}$
with the options~\option{--exposure-weight}, \option{--saturation-weight},
\option{--contrast-weight}, and \option{--entropy-weight} respectively.  The
functions~$f_{\mathrm{exp}}$, $f_{\mathrm{sat}}$, $f_{\mathrm{cont}}$, and $f_{\mathrm{ent}}$
along with the window sizes~$r_{\mathrm{cont}}$ and $r_{\mathrm{ent}}$ are explained in the next
sections.


\subsection[Weighted Average]{\label{sec:weighted-average}%
  \genidx{average!weighted}%
  \gensee{weighted average}{average, weighted}%
  Weighted Average}

By default, \App{} uses a weighted average, where \emph{each} pixel contributes as much as its
weight demands.  Of course the weights can be extreme, favoring only a few pixels or even only
one pixel in the input stack.  Extremes are not typical, however.

Equal weights are another extreme that turns \eqnref{equ:weight} into an arithmetic average.
This is why we sometimes speak of the ``averaging property'' of this weighting algorithm, like
smoothing out noise.


\subsection[Disabling Averaging]{\label{sec:disabling-averaging}%
  \genidx{average!disabling}%
  \gensee{disabling average}{average, disabling}%
  \optidx{--hard-mask}%
  Disabling Averaging: Option~\sample{--hard-mask}}

The weighted average computation as described above has proven to be widely successful with the
exception of one special case: focus stacking, where the averaging noticeably softens the final
image.

Use \sample{--hard-mask} to switch \App{} into a different weighting mode, where the pixel with
the highest weight wins, this is, gets weight~one, and all other pixels get the weight of zero.
With option~\option{--hard-mask} \eqnref{equ:weight} becomes
\[                              % equ:weight-hard-mask
    P(i, x, y) \rightarrow Q(x, y),
\]
where
\[
    w(P(i, x, y)) \geq w(P(j, x, y)) \quad \mbox{for all}\quad 1 \leq j \leq n.
\]
\noindent Note that this ``averaging'' scheme lacks the nice noise-reduction property of the
weighted average~\eqnref{equ:weight}, because only a single input pixel contributes to the
output.


\subsection[Single Criterion Fusing]{\label{sec:single-criterion-fusing}%
  \genidx{fusing!single criterion}%
  \gensee{single criterion fusing}{fusing, single criterion}%
  Single Criterion Fusing}

\App{} allows the user to weight each pixel of an input image by up to four different criteria
(see e.g.\ \chapterName~\fullref{sec:overview}).  However, it does not force the user to do so.
For some applications and more often simply to gain further insight into the weighting and
fusing process, looking at only a single criterion is the preferred way to work.

\genidx{criteria!active}%
\gensee{active criteria}{criteria, active}%
The version of \App{} for which this documentation was prepared, uses the default weights as
stated in \tableName~\ref{tab:default-weights}.  Notice that by default \emph{more than one}
weight is larger than zero, which means they are \emph{active}.


\begin{table}
  \centering
  \begin{tabular}{lc}
    \hline
    \multicolumn{1}{c|}{Criterion} & Default Weight \\
    \hline\extraheadingsep
    Exposure       & \val{val:default-weight-exposure} \\
    Saturation     & \val{val:default-weight-saturation} \\
    Local Contrast & \val{val:default-weight-contrast} \\
    Local Entropy  & \val{val:default-weight-entropy}
  \end{tabular}

  \caption[Default weights]{\label{tab:default-weights}%
    \genidx{weights!default}%
    \genidx{default weights}{weights, default}%
    \App{}'s default weights as compiled into \app.}
\end{table}


To disable a particular criterion set its weight to zero as for example

\begin{terminal}
  \$ \app{} \bslash \\
  ~~~~--exposure-weight=1 --saturation-weight=0 \bslash \\
  ~~~~--contrast-weight=0 --entropy-weight=0 \bslash \\
  ~~~~image\_[1-3].png
\end{terminal}

instructs \App{} to consider only the exposure weight.  Combine this with
option~\option{--save-masks} and it will become clearer how \App{} computes the exposure weight
for the set of images.

\genidx{criteria!overpowering one another}%
\genidx{overpowering criteria}{criteria, overpowering}%
Another problem that can be inspected by fusing with just a single active criterion and saving
the masks is if the weights of one criterion completely overpower all others.

\input{enfuse-exposure-weighting}
\input{enfuse-saturation-weighting}
\input{enfuse-local-contrast-weighting}
\input{enfuse-local-entropy-weighting}

\genidx[\rangeendlocation]{weighting functions}


%%% Local Variables:
%%% fill-column: 96
%%% End:
