%% This file is part of Enblend.
%% Licence details can be found in the file COPYING.


\chapter[Overview]{\label{sec:overview}%
  \genidx[\rangebeginlocation]{overview}%
  Overview}

\genidx{Mertens@\propername{Mertens, Tom}}%
\genidx{Kautz@\propername{Kautz, Jan}}%
\genidx{Reeth@\propername{Van Reeth, Frank}}%
\genidx{fusion!exposure}%
\gensee{exposure fusion}{fusion, exposure}%
\genidx{high dynamic range}%
\gensee{HDR@\acronym{HDR}}{high dynamic range}%
\begin{sloppypar}
  \App{} merges overlapping images using the
  \propername{Mertens}-\propername{Kautz}\-\propername{Van Reeth} exposure fusion
  algorithm.\footnotemark{} This is a quick way for example to blend differently exposed images
  into a nice output image, without producing intermediate high-dynamic range (\acronym{HDR})
  images that are then tone-mapped to a viewable image.  This simplified process often works much
  better than tone-mapping algorithms.%
  %
  \footnotetext{\propername{Tom Mertens}, \propername{Jan Kautz}, and \propername{Frank van
      Reeth}, ``Exposure Fusion'', Proceedings of the 15$^{\mathrm{th}}$ Pacific Conference on
    Computer Graphics and Applications 2007, pages~382--390.}
\end{sloppypar}

\genidx{depth-of-field}%
\gensee{DoF@\acronym{DoF}}{depth-of-field}%
\App{} can also be used to build extended depth-of-field (\acronym{DoF}) images by blending a
focus stack.

The idea is that pixels in the input images are weighted according to qualities such as, for
example, proper exposure, good local contrast, or high saturation.  These weights determine how
much a given pixel will contribute to the final image.

\genidx{Burt@\propername{Burt, Peter J.}}%
\genidx{Adelson@\propername{Adelson, Edward H.}}%
\genidx{Burt-Adelson@\propername{Burt-Adelson}}%
\genidx{multi-resolution spline}%
\gensee{spline}{multi-resolution spline}%
A \propername{Burt}-\propername{Adelson} multi-resolution spline blender\footnotemark{} is used
to combine the images according to the weights.  The multi-resolution blending ensures that
transitions between regions where different images contribute are difficult to spot.%
%
\footnotetext{\propername{Peter J. Burt} and \propername{Edward H. Adelson}, ``A Multiresolution
  Spline With Application to Image Mosaics'', \acronym{ACM} Transactions on Graphics,
  \abbreviation{Vol}.~2, \abbreviation{No}.~4, October~1983, pages~217--236.}

\App{} uses up to four criteria to judge the quality of a pixel:

\begin{description}
  \genidx{weighting!exposure}%
  \gensee{exposure weighting}{weighting, exposure}%
\item[Exposure]\itemend
  The exposure criteria favors pixels with luminance close to the middle of the range.  These
  pixels are considered better exposed than those with high or low luminance levels.

  \genidx{weighting!saturation}%
  \gensee{saturation weighting}{weighting, saturation}%
\item[Saturation]\itemend
  The saturation criteria favors highly-saturated pixels.  Note that saturation is only defined
  for color pixels.

  \genidx{weighting!local contrast}%
  \gensee{contrast weighting}{weighting, local contrast}%
  \gensee{local contrast weighting}{weighting, local contrast}%
\item[Local Contrast]\itemend
  The contrast criteria favors pixels inside a high-contrast neighborhood.  \App{} can use
  standard deviation, \propername{Laplacian} magnitude, or a blend of both as local contrast
  measure.

  \genidx{weighting!local entropy}%
  \gensee{entropy weighting}{weighting, local entropy}%
  \gensee{local entropy weighting}{weighting, local entropy}%
\item[Local Entropy]\itemend
  The entropy criteria prefers pixels inside a high-entropy neighborhood.  In addition, \App{}
  allows the user to mitigate the problem of noisy images when using entropy weighting by
  setting a black threshold.
\end{description}

\noindent See \tableName~\ref{tab:default-weights} for the default weights of these criteria.

For the concept of pixel weighting, and details on the different weighting functions, see
\chapterName~\fullref{sec:weighting-functions}.

Adjust how much importance is given to each criterion by setting the weight parameters on the
command line.  For example, if you set
\begin{literal}
  --exposure-weight=1.0 --saturation-weight=0.5
\end{literal}
\App{} will favor well-exposed pixels over highly-saturated pixels when blending the source
images.  The effect of these parameters on the final result will not always be clear in advance.
The quality of the result is subject to your artistic interpretation.  Playing with the weights
may or may not give a more pleasing result.  The authors encourage the users to experiment,
perhaps using down-sized or cropped images for speed.

\begin{geeknote}
  Down-sizing (also called ``down-sampling'') with a good interpolator reduces noise, which
  might not be desired to judge the image quality of the original-size image.  Cropping can
  offer an alternative, though.
\end{geeknote}

\genidx{channel!alpha}%
\gensee{alpha channel}{channel, alpha}%
\App{} expects but does not require each input image to have an alpha channel.  By setting the
alpha values of pixels to zero, users can manually remove those pixels from consideration when
blending.  If an input image lacks an alpha channel, \App{} will issue a warning and continue
assuming all pixels should contribute to the final output.  Any alpha value other than zero is
interpreted as ``this pixel should contribute to the final image''.

The input images are processed in the order they appear on the command line.  Multi\hyp{}layer
images are processed from the first layer to the last before \App{} considers the next image on
the command line.  Consult \sectionName~\ref{sec:layer-selection} on how to change the images'
order within multi\hyp{}layer image files.

\genidx{SourceForge}%
Find out more about \App{} on its \uref{\sourceforgenet}{SourceForge}
\uref{\enblendsourceforgenet}{web page}.

\genidx[\rangeendlocation]{overview}


%%% Local Variables:
%%% fill-column: 96
%%% End:
